Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-13 doc/manuscript/ESSDmanuscript.tex
knit

\caption{\label{tab:table_pools}\textbf{IPCC-defined forest carbon pools with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{pool} & \textbf{definition} & \textbf{important sources of estimate variation} & \textbf{IPCC guidance}\\
\hline
aboveground biomass & all biomass of living vegetation & min dbh & may exclude understory if minor component\\
\hline
 &  & include non-dicot trees? & ?\\
\hline
 &  & include dead standing? & no\\
\hline
 &  & biomass allometry & ?\\
\hline
belowground biomass & all biomass of live roots & all factors relevant to aboveground biomass & see above\\
\hline
 &  & allometry or assumed ratio of below- to above-ground biomass (R) & can estimate based on R\\
\hline
 &  & min root diameter & may exclude fine roots\\
\hline
 &  & sampling depth & ?\\
\hline
dead wood & all non-living woody biomass not contained in the litter, either standing, lying on the ground, or in the soil & min diameter & 10 cm default, but may be chosen by country\\
\hline
 &  & include belowground? & \vphantom{1} yes\\
\hline
litter & all non-living biomass with a size greater than the limit for soil organic matter  and less than the minimum diameter chosen for dead wood, lying dead, in various states of decomposition above or within the mineral or organic soil & max diameter (= max diameter for deadwood) & 10 cm default, but may be chosen by country\\
\hline
 &  & layers included & includes entire O horizon\\
\hline
 &  & include belowground? & yes\\
\hline
soil organic matter & organic carbon in mineral soils to a specified depth & sampling depth & 30 cm default, but may be chosen by country\\
\hline
\end{tabu}
\end{table}

>>>>

\caption{\label{tab:table_pools}\textbf{IPCC-defined forest carbon pools with definitions and measurement methods.} Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{pool} & \textbf{definition} & \textbf{important sources of estimate variation} & \textbf{IPCC guidance}\\
\hline
aboveground biomass & all biomass of living vegetation & min dbh & may exclude understory if minor component\\
\hline
 &  & include non-dicot trees? & ?\\
\hline
 &  & include dead standing? & no\\
\hline
 &  & biomass allometry & ?\\
\hline
belowground biomass & all biomass of live roots & all factors relevant to aboveground biomass & see above\\
\hline
 &  & allometry or assumed ratio of below- to above-ground biomass (R) & can estimate based on R\\
\hline
 &  & min root diameter & may exclude fine roots\\
\hline
 &  & sampling depth & ?\\
\hline
dead wood & all non-living woody biomass above a specified diameter, aboveground or belowground & min diameter & 10 cm default, but may be chosen by country\\
\hline
 &  & include belowground? & \vphantom{1} yes\\
\hline
litter & all non-living biomass with a size greater than the limit for soil organic matter  and less than the minimum diameter chosen for dead wood, lying dead, in various states of decomposition above or within the mineral or organic soil & max diameter (= max diameter for deadwood) & 10 cm default, but may be chosen by country\\
\hline
 &  & layers included & includes entire O horizon\\
\hline
 &  & include belowground? & yes\\
\hline
soil organic matter & organic carbon in mineral soils to a specified depth & sampling depth & 30 cm default, but may be chosen by country\\
\hline
\end{tabu}
\end{table}
